---
title: "socceranalysisR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{socceranalysisR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("UBC-MDS/socceranalysisR")
library(socceranalysisR)
```

Suppose you have three soccer data set:
```{r}
small_data_1 <- data.frame(age = - c(18, 20, 20, 25, 25, 24, 25, 30, 33, 32, 44, 30, 17),
                         Wages_Euros = c(300000, 575000,    150000, 475000,375000,  225000, 225000, 200000, 225000, 250000, 250000, 375000, 200000))
small_data_2 <- data.frame (Name  = c("Flora", "Mary", "Sarah", "Ester", "Sophie", "Maria"),
second_column = c(1, 4, 3, 5, 1, 6),
third_column  = c(7, 30, 12, 17, 34,8))
 
small_data_3 <- data.frame(Team=  c("A", "B", "B", "B", "C", "C") ,
                       Market_Value_Euros = c(375000,   225000, 225000, 200000, 225000, 250000),
                       age = c(18, 20, 20, 25, 25, 24)) 

```

## Generates meaningful visualizations to help users understand and interpret the numerical data using `soc_viz_stats`

You can view any two chosen columns in a binned scatter plots by:
```{r}
## scatter plots
soc_viz_stats('age', 'Wages_Euros', T , small_data_1)
```

Or you can view the distribution them as two histograms:
```{r}
## histograms
soc_viz_stats('age', 'Wages_Euros', FALSE , small_data_1)
```

## Identifes outliers using statistical methods using `soc_get_outliers`

You can also get the outliers based on standard deviations methods:
```{r}
## getting outliers
soc_get_outliers(small_data_1,Wages_Euros,"SD",2)
```

## Ranks players based on specific attributes with `soc_rankingplayers`

You can also rank players by their names based on the second feature by:
```{r}
# ranking players 
rankingplayers(small_data_2, "second_column")
```

## provides a quick and easy way to understand the descriptive statistics of a team with `soc_find_team_stat`

Finally, you can view a team's descriptive statistics table and box-plot of selected feature:
```{r}
# descriptive statistics
soc_find_team_stat(small_data_3, "B", Market_Value_Euros)
```


